---
title: "The reference scenario"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(ggplot2)
library(DiagrammeR)
library(kableExtra)
library(dplyr)
library(mvtnorm)
library(mc2d)
library(MASS)
library(survival)
library(fitdistrplus)
```

# Input data

In view of the all parameters described above, based on literature data, expert knowledge and investigations, a set of the most likely parameter values was set to define a reference scenario. These parameter values, set by default as input of all model computations, constitutes then references for further comparative analyses such as simulation convergence check, parameter sensitivity analyses or scenario simulations. All default values are gathered in @tbl-parameters-reference. This reference scenario was characterized by computing the virus transmission between workers, surfaces and meat portions in a processing plant from one initial infected worker during 42 days with five-minute time steps.

```{r}
#| label: tbl-parameters-reference
#| tbl-cap: 'Parameters values implemented for the reference scenario.'
data <- read.csv("csv/parameters_reference.csv",sep=";",header = F)
tabcolnames <- data[1, ]
data <- as.data.frame(data[-1,])
row.names(data) <- 1:nrow(data)
knitr::kable(
 data,
 col.names = tabcolnames) %>%
 kable_styling('striped', font_size = 11)
```

# Output indicators

list of input indicators

# Computing

## Parallel computing

## Convergence check

# Some results
